The Adaptive Multi-scale Simulation Infrastructure - Design and Implementation of a soft tissue simulation

### 2016-01-05 doc/articles/amsi_biotissue/paper.tex
working on paper

While implementation of desired numerical operations into a framework is of course possible, it may prove an additional undesirable overhead for an application programmer interested only in utilizing the multi-scale framework to implement simulation, rather than implementing the various numerical operations often perfected in widely available packages and libraries \cite{} \cite{} \cite{}.

@@

All communication and planning operations in the amsi libraries use an implicit local numbering for data distribution terms, essentially denoted by the term's index in a serialized communication buffer.

>>>>

Implementing required numerical operations inside an existing framework is of course possible, though it may prove an additional -- undesirable overhead for an application programmer interested only in utilizing the multi-scale framework to implement a simulation, rather than implementing the various numerical operations often optimized in widely available packages and libraries.

@@

All communication and planning operations in the amsi libraries use an implicit local numbering for data distribution terms, the index associated with the term in a local serialized buffer.
